Improving Haskell Types with SMT

### 2015-07-18 docs/paper.tex
Embed the bibliography

\bibliographystyle{abbrvnat}
\bibliography{refs}

% 
% % The bibliography should be embedded for final submission.
% 
% \begin{thebibliography}{}
% \softraggedright
% 
% \bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
% P. Q. Smith, and X. Y. Jones. ...reference text...
% 
% \end{thebibliography}

>>>>

% \bibliographystyle{abbrvnat}
% \bibliography{refs}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{}
\softraggedright

\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[yic(2015)]{yices}
\emph{Yices Manual}, 2015.
\newblock URL \url{http://yices.csl.sri.com/papers/manual.pdf}.

\bibitem[{Adam Gundry}(2015)]{units-of-measure}
{Adam Gundry}.
\newblock A typechecker plugin for units of measure.
\newblock Submitted for publication., 2015.

\bibitem[{Christiaan Baaij}(2015)]{typelits-normalise}
{Christiaan Baaij}.
\newblock A plug-in for normalising type literals in ghc.
\newblock 2015.
\newblock URL \url{https://github.com/clash-lang/ghc-typelits-natnormalise}.

\bibitem[{Clark Barrett} et~al.(2010){Clark Barrett}, {Aaron Stump}, and
  {Cesare Tinelli}]{smtlib2}
{Clark Barrett}, {Aaron Stump}, and {Cesare Tinelli}.
\newblock The {SMT-LIB} standard: Version 2.0.
\newblock Technical report, Department of Computer Science, The University of
  Iowa, 2010.
\newblock URL
  \url{http://smtlib.cs.uiowa.edu/papers/smt-lib-reference-v2.0-r12.09.09.pdf}.

\bibitem[{Clark Barrett} et~al.(2011){Clark Barrett}, {Christopher L. Conway},
  {Morgan Deters}, {Liana Hadarean}, {Dejan Jovanovi\'{c}}, {Tim King}, {Andrew
  Reynolds}, and {Cesare Tinelli}]{cvc4}
{Clark Barrett}, {Christopher L. Conway}, {Morgan Deters}, {Liana Hadarean},
  {Dejan Jovanovi\'{c}}, {Tim King}, {Andrew Reynolds}, and {Cesare Tinelli}.
\newblock {CVC4}.
\newblock In \emph{Proceedings of the 23rd International Conference on Computer
  Aided Verification}, Snowbird, Utah, USA, 2011.
\newblock URL \url{http://dl.acm.org/citation.cfm?id=2032305.2032319}.

\bibitem[{Dimitrios Vytiniotis} and {Simon Peyton Jones}(2013)]{fc-evidence}
{Dimitrios Vytiniotis} and {Simon Peyton Jones}.
\newblock Evidence normalization in System FC.
\newblock In \emph{24th International Conference on Rewriting Techniques and
  Applications}, Eindhoven, Netherlands, 2013.
\newblock URL
  \url{http://research.microsoft.com/en-us/um/people/simonpj/papers/ext-f/fc-new-tyco.pdf}.

\bibitem[{Dimitrios Vytiniotis} et~al.(2011){Dimitrios Vytiniotis}, {Simon
  Peyton Jones}, {Tom Schrijvers}, and {Martin Sulzmann}]{outsidein}
{Dimitrios Vytiniotis}, {Simon Peyton Jones}, {Tom Schrijvers}, and {Martin
  Sulzmann}.
\newblock {OutsideIn(X)}: Modular type inference with local assumptions.
\newblock \emph{Journal of Functional Programming}, September 2011.
\newblock URL
  \url{http://research.microsoft.com/apps/pubs/default.aspx?id=162516}.

\bibitem[{Greg Nelson} and {Derek C. Oppen}(1979)]{NelsonOppen}
{Greg Nelson} and {Derek C. Oppen}.
\newblock Simplification by cooperating decision procedures.
\newblock \emph{ACM Transactions on Programming Languages and Systems},
  1\penalty0 (2), October 1979.
\newblock URL \url{http://doi.acm.org/10.1145/357073.357079}.

\bibitem[{Iavor S. Diatchki}(2015{\natexlab{a}})]{simple-smt}
{Iavor S. Diatchki}.
\newblock \emph{simple-smt: a {Haskell} library for working with SMT solvers},
  2015{\natexlab{a}}.
\newblock URL \url{http://hackage.haskell.org/package/simple-smt}.

\bibitem[{Iavor S. Diatchki}(2015{\natexlab{b}})]{type-nats-solver}
{Iavor S. Diatchki}.
\newblock A plug-in for solving linear constraints using an smt solver.
\newblock 2015{\natexlab{b}}.
\newblock URL \url{https://github.com/yav/type-nat-solver}.

\bibitem[{J. Garrett Morris} and {Mark P. Jones}(2010)]{instance-chains}
{J. Garrett Morris} and {Mark P. Jones}.
\newblock Instance chains: Type class programming without overlapping
  instances.
\newblock In \emph{Proceedings of the 15th ACM SIGPLAN International Conference
  on Functional Programming (ICFP '10)}, Baltimore, Maryland, USA, 2010.
\newblock URL \url{http://web.cecs.pdx.edu/~mpj/pubs/instancechains.pdf}.

\bibitem[{Leonardo de Moura} and {Nikolaj Bjørner}(2008)]{z3}
{Leonardo de Moura} and {Nikolaj Bjørner}.
\newblock Z3: An efficient smt solver.
\newblock In \emph{Tools and Algorithms for the Construction and Analysis of
  Systems, 14th International Conference}, Budapest, Hungary, 2008.
\newblock URL \url{http://research.microsoft.com/projects/z3/z3.pdf}.

\bibitem[{Mark P. Jones}(1995)]{improvement}
{Mark P. Jones}.
\newblock Simplifying and improving qualified types.
\newblock In \emph{FPCA '95: Conference on Functional Programming Languages and
  Computer Architecture}, La Jolla, California, USA, 1995.
\newblock URL \url{http://web.cecs.pdx.edu/~mpj/pubs/fpca95.pdf}.

\bibitem[{Niki Vazou} et~al.(2014){Niki Vazou}, {Eric L. Seidel}, {Ranjit
  Jhala}, {Dimitrios Vytiniotis}, and {Simon Peyton-jones}]{liquid-haskell}
{Niki Vazou}, {Eric L. Seidel}, {Ranjit Jhala}, {Dimitrios Vytiniotis}, and
  {Simon Peyton-jones}.
\newblock Refinment types for Haskell.
\newblock In \emph{Proceedings of the 19th ACM SIGPLAN International Conference
  on Functional Programming}, Gothenburg, Sweeden, 2014.
\newblock URL
  \url{http://goto.ucsd.edu/~rjhala/papers/refinement_types_for_haskell.pdf}.

\bibitem[{Patrick C. Hickey} et~al.(2014){Patrick C. Hickey}, {Lee Pike},
  {Trevor Elliott}, {James Bielman}, and {John Launchbury}]{ivory-experience}
{Patrick C. Hickey}, {Lee Pike}, {Trevor Elliott}, {James Bielman}, and {John
  Launchbury}.
\newblock Building embedded systems with embedded {DSLs} (experience report).
\newblock In \emph{Proceedings of the 2014 ACM SIGPLAN Conference on Functional
  Programming}, Gothenburg, Sweden, 2014.
\newblock URL
  \url{https://github.com/GaloisInc/smaccmpilot-experiencereport/blob/master/embedded-experience.pdf?raw=true}.

\bibitem[{Richard A. Eisenberg} and {Jan Stolarek}(2014)]{Eisenberg2014}
{Richard A. Eisenberg} and {Jan Stolarek}.
\newblock Promoting functions to type families in {Haskell}.
\newblock In \emph{Proceedings of the 2014 ACM SIGPLAN Symposium on {Haskell}},
  Gothenburg, Sweden, 2014.
\newblock URL
  \url{http://www.cis.upenn.edu/~eir/papers/2014/promotion/promotion.pdf}.

\bibitem[{Richard A. Eisenberg} and {Stephanie Weirich}(2012)]{Eisenberg2012}
{Richard A. Eisenberg} and {Stephanie Weirich}.
\newblock Dependently typed programming with singletons.
\newblock In \emph{Proceedings of the 2012 ACM SIGPLAN Symposium on {Haskell}},
  Copenhagen, Denmark, 2012.

\bibitem[{Sam Lindley} and {Conor McBride}(2013)]{Lindley2013}
{Sam Lindley} and {Conor McBride}.
\newblock Hasochism: The pleasure and pain of dependently typed {Haskell}
  programming.
\newblock In \emph{Proceedings of the 2013 ACM SIGPLAN Symposium on {Haskell}},
  Boston, Massachusetts, USA, 2013.
\newblock URL
  \url{https://personal.cis.strath.ac.uk/conor.mcbride/pub/hasochism.pdf}.

\bibitem[{Sergey Berezin} et~al.(2003){Sergey Berezin}, {Vijay Ganesh}, and
  {Daivd L. Dill}]{cvc4-lin-arith}
{Sergey Berezin}, {Vijay Ganesh}, and {Daivd L. Dill}.
\newblock An online proof-producing decision procedure for mixed-integer linear
  arithmetic.
\newblock In \emph{Proceedings of the 9th International Conference on Tools and
  Algorithms for the Construction and Analysis of Systems}, Warsaw, Poland,
  2003.
\newblock URL \url{http://hci.stanford.edu/cstr/reports/2007-07.pdf}.

\bibitem[{The GHC Team}(2015)]{ghc-manual}
{The GHC Team}.
\newblock \emph{The Glorious Glasgow Haskell Compilation System User's Guide,
  Version 7.10.1}, 2015.
\newblock URL
  \url{https://downloads.haskell.org/~ghc/7.10.1/docs/html/users_guide/index.html}.

\end{thebibliography}
